---
title: "Final Project"
author: "Danyang Chen"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Read in data
library(ggplot2)
library(esquisse)
library(haven)
library(plotly)
library(DT)
library(dplyr)

client_exit_raw <- read_dta("care/Client Exit.dta")

client_exit <- client_exit_raw %>%
  select(sex,age, Region,Zone,HH_ID,HC_type,quick_consult,consult_time,treatment_type,listining,ask,full_info,
         access_help,confidentiality,SRH,recommend) %>%
  filter(sex=="female")
client_exit <- na.omit(client_exit)
client_exit <- client_exit %>%
  mutate(across(everything(), haven::as_factor))

# Create Privacy and Confidentiality Score (0-5)
client_exit$Privacy_Confidentiality_Score <- rowSums(client_exit[, c("listining", "ask", "full_info", 
                                                   "access_help", "confidentiality")] == "Yes")

# Create SRH Service Utilization Score (0-5)
client_exit$SRH_Utilization_Score <- rowSums(client_exit[, c("quick_consult", "consult_time", "treatment_type",
                                           "SRH", "recommend")] == "Yes")

# Rename columns for readability 
client_exit <- client_exit %>% 
  rename(
    `Zone Name` = Zone,
    `Health Center Type` = HC_type,
    `Recommendation` = recommend,
    `Confidentiality Score` = confidentiality,
    `Privacy and Confidentiality Score` = Privacy_Confidentiality_Score,
    `Sexaul and Reproductive Health Service Utilization Score` = SRH_Utilization_Score,
  )

client_exit <- client_exit %>% 
  mutate(`Zone Name` = case_when(
    `Zone Name` == "East_H" ~ "East Haraghe",
    `Zone Name` == "West_H" ~ "West Haraghe",
    `Zone Name` == "Zone_3" ~ "Zone 3",
    TRUE ~ as.character(`Zone Name`)
  ))

# Process data: Calculate satisfaction percentage and summary stats
client_exit_summary <- client_exit %>%
  group_by(Region, `Zone Name`, `Health Center Type`) %>%
  summarise(
    Satisfied_Pct = mean(`Recommendation` == "Yes", na.rm = TRUE) * 100,
    Privacy_Mean = mean(`Privacy and Confidentiality Score`, na.rm = TRUE),
    Privacy_Median = median(`Privacy and Confidentiality Score`, na.rm = TRUE)
  )
```

# Dataset Visualization

Access GitHub page here: https://github.com/danyangc/flexdashboard

**Widget 1: Interactive Bar Chart**

```{r, echo=FALSE}
p <- ggplot(client_exit_summary, aes(x = Region, y = Satisfied_Pct, fill = `Health Center Type`, text = paste(
  "Zone Name:", `Zone Name`, "<br>",
  "Satisfied %:", round(Satisfied_Pct, 2), "<br>",
  "Mean Privacy Score:", round(Privacy_Mean, 2), "<br>",
  "Median Privacy Score:", round(Privacy_Median, 2)
))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(title = "Client Satisfaction Across Regions and Facility Types",
       x = "Region", y = "Satisfied Clients (%)") +
  theme_minimal()

# Convert to plotly for interactivity
plotly::ggplotly(p, tooltip = "text")

```

**Key Takeaways from Widget 1**

-   Clients in **Zonal Hospitals** report consistently **high satisfaction levels (100%)**, with higher privacy means, particularly in **East Haraghe (4.5)** and **Zone 3 (4.0)**.
-   **Health centers in East Haraghe** show a lower satisfaction rate (**75%**) and a lower privacy mean (**3.13**), indicating potential privacy concerns.
-   The lowest privacy perception is in **West Haraghe Zonal Hospital (1.0)**, despite a **100% satisfaction rate**, suggesting that satisfaction may not always correlate with perceived privacy.

Row {data-width=650}
----------------------------------

**Widget 2: Interactive Data Table**

Row {data-width=650}
----------------------------------

```{r, echo=FALSE}
DT::datatable(
  client_exit %>% select(age, Region, `Zone Name`, `Health Center Type`, `Privacy and Confidentiality Score`, `Sexaul and Reproductive Health Service Utilization Score`, Recommendation),
  filter = "top",
  options   = list(
    pageLength = 10,
    autoWidth  = TRUE,
    scrollY    = 380,
    paging     = FALSE
  )
)
```

Row {data-width=650}
----------------------------------

**Key Takeaways from Widget 2**

Row {data-width=650}
----------------------------------

-   Privacy perception scores impact service recommendations **higher privacy scores usually align with higher satisfaction levels**

-   **West Haraghe Zonal Hospital** has only **one client** in the dataset, which limits broader conclusions, but this client reported low privacy perception (1.0) despite 100% satisfaction.

Row {data-width=650}
----------------------------------

**Real-world impact** This dashboard highlights privacy-related gaps in SRH services for Ethiopian adolescents. Findings can help inform targeted improvements in service delivery across different regions in Ethiopia.


# Dataset Description

**Dataset Information**

The dataset was collected in February 2024 as part of a baseline assessment for the “Uplift Her” project, by CARE Ethiopia. It includes responses from 29 adolescent girls who completed a clinic exit survey after receiving health services. The survey was conducted in Afar and Oromia regions by trained staff from BAN – Development Research Center for Excellence (BAN-DRCE). Data were collected through face-to-face interviews and entered digitally in .dta (Stata) format. The dataset is confidential and not publicly available due to the sensitivity of the information collected.
